---
title: "Paternal effects research: synthesis of evidence, influence and opportunities "
author: "Joanna Rutkowska, Malgorzata Lagisz, Russell Bonduriansky, Shinichi Nakagawa"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_download: true
    code_folding: hide
    depth: 4
    number_sections: no
    theme:  cosmo # “default”, “cerulean”, “journal”, “flatly”, “darkly”, “readable”, “spacelab”, “united”, “cosmo”, “lumen”, “paper”, “sandstone”, “simplex”, “yeti”
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
subtitle: Electronic Supplementary Material
bibliography: references.bib
#biblio-style: "apalike"
csl: nature.csl
link-citations: yes
---

```{r setup, include = FALSE}
#kniter seetting
knitr::opts_chunk$set(
message = FALSE,
warning = FALSE, # no warnings
cache = TRUE,# Cacheing to save time when kniting
tidy = TRUE
#fig.width = 9
)

# clearning up
rm(list=ls())
```

## Setups

### Loading packages and custom functions

```{r}
# loading packages
# devtools::install_github("thomasp85/patchwork")
pacman::p_load(   tidyverse, # tidy family and related pacakges below
                  magrittr, # extending piping
                  ggbeeswarm, # making bee-swarm plots possible
                  plotly,     # interactive plots using ggplot2
                  fulltext, 
                  dplyr, 
                  tidyr, 
                  readxl, 
                  janitor, 
                  bibliometrix, 
                  DescTools,
                  ggplot2, 
                  easyalluvial
)
library(readxl)

install.packages("bibliometrix", dependencies=TRUE) 
library(bibliometrix) 

install.packages("easyalluvial")
library(easyalluvial)
install.packages("dplyr")
library(dplyr)
library(plyr)

```

#### Custom functions

We have no custom functions named : xx, , all of which are used later (see below for their functionality) and the code are included here. 

```{r}
# coustm functions

#' Title: xx 
# 

```

## Preparations of the data files

```{r}
# Getting the main data files

empirical <- read_excel("2019-07-11-fulltext-empirical-included.xlsx")
View(empirical)
names(empirical)


nonempirical <- read_excel("2019-05-25-fulltext-codes-nonempirical-included.xlsx")
View(nonempirical)
names(nonempirical)

#changing variable names in the non-empirical file
nonempirical<- nonempirical %>% rename(
  Doi = "copy & paste doi",
  Form = "What publication form does the record have?", 
  Type = "What type of paper is it or claims to be?", 
  Taxon = "What is its taxonomic scope?", 
  Primary_focus = "What is its primary focus?", 
  Secondary_focus = "What is its secondary focus?")

colnames(nonempirical)[12] <- "primary_other"
colnames(nonempirical)[14] <- "secondary_other"
names(nonempirical)


```



## Cluster analysis (from VosViewer), after Nettle 2019:

```{r}
# Read in map and cluster files created by VOS viewer
# Records included in our systematic review were searched for again in Scopus database on 16th September 2019. Together with their citaions, they were uplodaed to VOSViewer. VOSViewer indietified that the records are grouped in 3 clusters and created two files (network and map) which are uplodaed here.

network <- read.delim(file = "2019-09-16-3cl-networktrial.txt", header = TRUE, sep = "\t", dec = ".")
str(network)
network %>% rename(from.id = ď.ż1, to.id = X8 , links = X0.0227) -> network
str(network)

map <- read.delim("2019-09-16-3cl-maptrial.txt")
str(map)
map %>% rename(id = ď.żid) -> map
str(map)

# Make matrix of connections
clusters <- select(map, id, cluster)
str(clusters)

d <- merge(network, clusters, by.x="from.id", by.y="id")
d <- merge(d, clusters, by.x="to.id", by.y="id")
parta <- xtabs(~d$cluster.x + d$cluster.y) 
partb <- t(parta)
link.matrix <- parta + partb
xtabs(~map$cluster)


# Numbers of papers per cluster
n <- as.vector(xtabs(~map$cluster))
n
str(n)

# Expected number of links
expected <- n%*%t(n)
diag(expected) <- diag(expected)-n
expected
f <- link.matrix/expected

# Make data frame of the connection indices
x <- c(rep("A1", times=3), rep("A2", times=3), rep("A3", times=3))
y <- rep(c("A1", "A2", "A3"), times=3)
z <- as.vector(f)
l <- data.frame(x, y, z)

# Assign names to cluster numbers
l$x <- as.character(l$x)
l$x[l$x == "A1"] <- "Med"
l$x[l$x == "A2"] <- "Tox"
l$x[l$x == "A3"] <- "EcoEvo"
l$y <- as.character(l$y)
l$y[l$y == "A1"] <- "Med"
l$y[l$y == "A2"] <- "Tox"
l$y[l$y == "A3"] <- "EcoEvo"

l$y <- factor(l$y, levels = c('Med','Tox','EcoEvo'))
l$x <- factor(l$x, levels = c('Med','Tox','EcoEvo'))

# Plot Figure showing connections between the clusters
figure=ggplot(l, aes(x=x, y=z, fill=x)) + 
  geom_bar(stat="identity") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  theme(legend.position = "none") +
  facet_grid(~y) + 
  xlab("Cluster") + 
  ylab("Connection index") + 
  scale_fill_discrete(name="Cluster") + 
  coord_cartesian(ylim=c(0, 0.5))+
theme(aspect.ratio=0.7)+
ggsave("Fig-3b.pdf")
```

## Merging data files with bibliometric clustering

```{r}
# Preparing empirical data file for merging the records based on Doi

empirical$Doi <- tolower(empirical$Doi)
empirical$Doi <- gsub("/", ".", empirical$Doi)
empirical$Doi <- gsub("-", ".", empirical$Doi) 
empirical$Doi <- gsub("–", ".", empirical$Doi) 
empirical$Doi <- gsub("_", ".", empirical$Doi) 
empirical$Title <- tolower(empirical$Title) 

# Puting title in the place of Doi (if there is no Doi)  in a new columen called link
empirical <- mutate(empirical, link = Doi)
empirical <- mutate(empirical,link = ifelse(Doi == "..", Title, link))


# Preparing map data (from VOSViewer) for merging records based on Doi 
map$url <- gsub("https://doi.org/", "", map$url)

map %>% rename(Doi = url) -> map
map$Doi <- tolower(map$Doi)
map$Doi <- gsub("/", ".", map$Doi)
map$Doi <- gsub("-", ".", map$Doi) 
map$Doi <- gsub("–", ".", map$Doi) 
map$Doi <- gsub("_", ".", map$Doi) 

map$description <- gsub(".*</td></tr><tr><td>Title:</td><td>(.+)</td></tr><tr><td>Source:</td><td>.*", "\\1", map$description)
map %>% rename(Title = description) -> map

## puting title in the place of Doi (if there is no Doi)  in a new columen called link
map <- mutate(map, link = Doi)
map <- mutate(map,link = ifelse(Doi == "", Title, link))


```

```{r adding cluster ID to empirical layer}

# Merging empirical data file with map file by doi 
empirical_clusters <- left_join(empirical, map, by="link")

# Saving file empirical_clusters
write.csv(empirical_clusters, 'empirical_clusters.csv')
clusters_assigned <- data.frame(xtabs(~cluster, empirical_clusters))

# Identifying records not assigned to clusters - needs fixing or removign
nocluster <- filter(empirical_clusters, is.na(empirical_clusters$cluster))

write.csv(nocluster, 'nocluster.csv')


```

## Bibilometric analysis aimimg at presenting number of citations 

```{r getting the data, merging information}
# NUmber of citaions is visualised for all paperes included in the systematic review. Thus, it is not restriced to the paperes assigend to clusters. 
# Records included in our systematic review were searched for in Scopus database on 23rd July 2019. This was done separatly for empircial and non-empirical paperes. In both cases, the papers, together with their citaions, were uplodaed here. 

# Getting the data from Scopus database for empirical layer
tmpE <- readFiles("2019-07-23-empiricalBib.bib")
bibE <- convert2df(tmpE, dbsource = "scopus", format = "bibtex") # Convert to a bibliometric data frame

names(bibE)
write.csv(bibE, "bibE_as_df.csv", row.names = FALSE)
str(bibE)


# Getting the data from Scopus database for non-empirical layer
tmpNE <- readFiles("2019-07-23-nonempiricalBib.bib")
bibNE <- convert2df(tmpNE, dbsource = "scopus", format = "bibtex") # Convert to a bibliometric data frame

names(bibNE)
write.csv(bibNE, "bibNE_as_df.csv", row.names = FALSE)
str(bibNE)


# For both layers, adding additional columns with layer label
bibE <-  mutate(bibE, map_layer = "empirical")
bibE <- mutate(bibE, BN = "NA")
bibNE <- mutate(bibNE, map_layer = "non_empirical")

# Joining data of both layers
bibE_NE <- union(bibE, bibNE)


```

```{r cleaning the data, saving file}
#  Cleaning records that cause trouble
grep("\\(NEOTIGASON/SORIATANE?", bibE_NE$TI)
bibE_NE$TI <- gsub("\\(NEOTIGASON/SORIATANE?","(NEOTIGASON/SORIATANE)?", bibE_NE$TI)

grep("NEOTIGASON/SORIATANE", bibE_NE$CR)
bibE_NE$CR[37]


bibE_NE$CR <- gsub("\\(NEOTIGASON/SORIATANE","(NEOTIGASON/SORIATANE)", bibE_NE$CR)


# Saving the file
write.csv(bibE_NE, "bibE_NE.csv", row.names = FALSE)
bibE_NE <- read.csv("bibE_NE.csv")

# map <- read.csv("map.csv") - not sure if this is the right place
```

```{r merging the file with cluster assigment, making figure}
# Preparing for joining of the file based on Doi
bibE_NE$Doi <- gsub("https://doi.org/", "", bibE_NE$DI)
bibE_NE$Doi <- tolower(bibE_NE$Doi)
bibE_NE$Doi <- gsub("/", ".", bibE_NE$Doi)
bibE_NE$Doi <- gsub("-", ".", bibE_NE$Doi) 
bibE_NE$Doi <- gsub("_", ".", bibE_NE$Doi) 


# Trying to get titlesto make the link - does not work!
summary(bibE_NE)

bibE_NE <- mutate(bibE_NE, link = Doi)
bibE_NE <- mutate(bibE_NE,link = ifelse(Doi == " ", TI, link))

# Joining based on Doi - but would be better to join based on lik!!!
joined <- left_join(bibE_NE, map, by = 'Doi')

# Preparing data for the figure
joined$cluster <- factor(joined$cluster)


joined$cluster <- as.character(joined$cluster)
joined$cluster[joined$cluster == "1"] <- "Med"
joined$cluster[joined$cluster == "2"] <- "Tox"
joined$cluster[joined$cluster == "3"] <- "EcoEvo"

joined$cluster <- factor(joined$cluster, levels = c('Med','Tox','EcoEvo'))

# Making figure showing total citation count (TC) according to publication year (PY) and map layer and cluster. Paperes not assigned to one of three clusters are in grey.

ggplot(joined, aes(x=PY, y=TC, color = cluster, shape = map_layer))+
                geom_point(size=4, alpha=0.6)+
        scale_size(guide="none")+
        scale_alpha(guide="none")+
       scale_x_continuous(breaks=c(1970,1980,1990,2000, 2010, 2020))+
        theme_classic()+
        labs(x= "Publication year", y = "Total citations")+
               theme_classic()+ 
  theme(legend.position = "none") +
  theme(aspect.ratio=0.45)+
  ggsave("Fig-3c.pdf")  

```



## Visulasiation of the empirical layer of the map

```{r Alluvial plot for the contence of empirical layer of the map}
# Preparing the data by separation multiply exposure into separate rows of data
empirical_clusters_expo <- empirical_clusters %>% separate_rows(Exposure_category, sep = "; ")

# Preparing the data by selecting the most important variables to be used in the plot
empirical_clusters_expo1 <- select(empirical_clusters_expo, Taxon, Source_of_population, Exposure_category, Maternal_exposure, Offspring_exposure, cluster)

# Changing duplicated names of categories
empirical_clusters_expo1$Taxon <- as.character(empirical_clusters_expo1$Taxon)
empirical_clusters_expo1$Taxon[empirical_clusters_expo1$Taxon == "human"] <- "men"

empirical_clusters_expo1$Maternal_exposure <- as.character(empirical_clusters_expo1$Maternal_exposure)
empirical_clusters_expo1$Maternal_exposure[empirical_clusters_expo1$Maternal_exposure == "no"] <- "none"

# separation into clusters and changing columns into factors
clusterMed <-subset(empirical_clusters_expo1, empirical_clusters_expo1$cluster=="1")
clusterTox <-subset(empirical_clusters_expo1, empirical_clusters_expo1$cluster=="2")
clusterEE <-subset(empirical_clusters_expo1, empirical_clusters_expo1$cluster=="3")

clusterMed$Taxon <-as.factor(clusterMed$Taxon)
clusterMed$Source_of_population <-as.factor(clusterMed$Source_of_population)
clusterMed$Exposure_category <-as.factor(clusterMed$Exposure_category)
clusterMed$Maternal_exposure <-as.factor(clusterMed$Maternal_exposure)
clusterMed$Offspring_exposure <-as.factor(clusterMed$Offspring_exposure)
clusterMed$cluster <-as.factor(clusterMed$cluster)

clusterTox$Taxon <-as.factor(clusterTox$Taxon)
clusterTox$Source_of_population <-as.factor(clusterTox$Source_of_population)
clusterTox$Exposure_category <-as.factor(clusterTox$Exposure_category)
clusterTox$Maternal_exposure <-as.factor(clusterTox$Maternal_exposure)
clusterTox$Offspring_exposure <-as.factor(clusterTox$Offspring_exposure)
clusterTox$cluster <-as.factor(clusterTox$cluster)

clusterEE$Taxon <-as.factor(clusterEE$Taxon)
clusterEE$Source_of_population <-as.factor(clusterEE$Source_of_population)
clusterEE$Exposure_category <-as.factor(clusterEE$Exposure_category)
clusterEE$Maternal_exposure <-as.factor(clusterEE$Maternal_exposure)
clusterEE$Offspring_exposure <-as.factor(clusterEE$Offspring_exposure)
clusterEE$cluster <-as.factor(clusterEE$cluster)

# Setting color pallets for each cluster for Figure 4a (fllows and starata have separate pallets)
col_vectorMed3a = c('Abiotic habitat'="#6b452b",'Age'="#6fa6ab",  'Alcohol'="#b0b54e", 'Chemical substance'= "#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d",'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c" )

col_vectorMed3b = c('human'="#828585",'domesticated'="gray55",'captive'="gray10", 'wild'= "gray60", 'men'="#828585",'non-human mammal'="gray5", 'fish'="gray15", 'other vertebrate'="gray25", 'other invertebrate'="gray35", 'plant'="gray45", 'Abiotic habitat'="#6b452b",'Age'="#6fa6ab",  'Alcohol'="#b0b54e", 'Chemical substance'= "#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d",'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c")


col_vectorTox3a = c('Abiotic habitat'="#6b452b",'Chemical substance'="#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d", 'Physiological factor'="#a2a39b")

col_vectorTox3b = c('human'="#828585", 'captive'="gray10", 'wild brought into captivity'="gray50",'men'="#828585",'non-human mammal'="gray5", 'arthropod'="gray40", 'Abiotic habitat'="#6b452b",'Chemical substance'="#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d", 'Physiological factor'="#a2a39b")


col_vectorEE3a = c('Abiotic habitat'="#6b452b",'Age'="#6fa6ab", 'Chemical substance'="#7081a1", 'Diet'="#edcb8a", 'Past experience'="#3a3e3f", 'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c")

col_vectorEE3b = c('captive'="gray10",  'wild brought into captivity'="gray50",'wild'="gray60", 'non-human mammal'="gray5", 'bird' = "gray30" , 'fish'="gray15", 'other vertebrate'="gray25",'arthropod' ="gray60" , 'other invertebrate'="gray35", 'plant'="gray45",'Abiotic habitat'="#6b452b",'Age'="#6fa6ab", 'Chemical substance'="#7081a1", 'Diet'="#edcb8a", 'Past experience'="#3a3e3f", 'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c")

# Setting color palets for each cluster for figure 4b 
col_vectorMed4 = c('Abiotic habitat'="#6b452b",'Age'="#6fa6ab",  'Alcohol'="#b0b54e", 'Chemical substance'= "#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d",'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c", 'none' = "black", 'independent' = "#828585", 'diallel' ="gray", 'NA' = "white", 'no'= "black", 'yes' = "gray")

col_vectorTox4 = c('Abiotic habitat'="#6b452b",'Chemical substance'="#7081a1",  'Diet'="#edcb8a", 'Drug'="#70697d", 'Physiological factor'="#a2a39b", 'none' = "black", 'independent' = "#828585", 'diallel' ="gray", 'no'= "black")

col_vectorEE4 = c('Abiotic habitat'="#6b452b",'Age'="#6fa6ab", 'Chemical substance'="#7081a1", 'Diet'="#edcb8a", 'Past experience'="#3a3e3f", 'Physiological factor'="#a2a39b",'Psychological factor'= "#1b1b1c", 'none' = "black", 'independent' = "#828585", 'diallel' ="gray", 'NA' = "white", 'no'= "black", 'yes' = "gray")



# Graphs 4a


allMed3 <-alluvial_wide(select(clusterMed, Source_of_population, Taxon, Exposure_category ), fill_by = 'last_variable', order_levels = c('human','domesticated','captive', 'wild', 'men','non-human mammal', 'fish', 'other vertebrate', 'other invertebrate', 'plant','Abiotic habitat','Age',  'Alcohol', 'Chemical substance',  'Diet', 'Drug','Physiological factor','Psychological factor'),stratum_label_size = 7, 
                        col_vector_flow = col_vectorMed3a, col_vector_value = col_vectorMed3b)+
  theme_classic()+
  theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
   labs(title= 'Med cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-Med-4a.pdf", scale = 6, width = 10, units=c("cm") )

allTox3 <- alluvial_wide(select(clusterTox, Source_of_population, Taxon, Exposure_category ), fill_by = 'last_variable',   order_levels = c('human', 'captive', 'wild brought into captivity','men','non-human mammal', 'arthropod' ), stratum_label_size = 7,
                        col_vector_flow = col_vectorTox3a, col_vector_value = col_vectorTox3b) + 
  theme_classic()+
 theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
  labs(title= 'Tox cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-Tox-4a.pdf", scale = 6, width = 10, units=c("cm"))

allEE3 <- alluvial_wide(select(clusterEE,Source_of_population, Taxon, Exposure_category ), fill_by = 'last_variable',  order_levels = c('captive',  'wild brought into captivity','wild','non-human mammal', 'bird', 'fish', 'other vertebrate','arthropod', 'other invertebrate', 'plant', 'Abiotic habitat','Age','Chemical substance',  'Diet', 'Past experience', 'Physiological factor','Psychological factor'), stratum_label_size = 7,
                        col_vector_flow = col_vectorEE3a, col_vector_value = col_vectorEE3b) +
  theme_classic()+
theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
  labs(title= 'EcoEvo cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-EE-4a.pdf", scale = 6, width = 10, units=c("cm") )

# Graphs 4b

allMed4 <-alluvial_wide(select(clusterMed, Exposure_category, Maternal_exposure, Offspring_exposure ), fill_by = 'first_variable', order_levels = c('Abiotic habitat','Age',  'Alcohol', 'Chemical substance',  'Diet', 'Drug','Physiological factor','Psychological factor', 'none' , 'independent' , 'diallel' , 'NA' , 'no' , 'yes' ), stratum_label_size = 7,
                       col_vector_flow = col_vectorMed4, col_vector_value = col_vectorMed4)+
  theme_classic()+
  theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
   labs(title= 'Med cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-Med-4b.pdf", scale = 6, width = 10, units=c("cm") )

allTox4 <- alluvial_wide(select(clusterTox, Exposure_category, Maternal_exposure, Offspring_exposure), fill_by = 'first_variable',   order_levels = c('Abiotic habitat', 'Chemical substance',  'Diet', 'Drug', 'Physiological factor', 'none', 'independent', 'diallel' , 'no' ), stratum_label_size = 7,
                        col_vector_flow = col_vectorTox4, col_vector_value = col_vectorTox4) + 
  theme_classic()+
 theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
   labs(title= 'Tox cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-Tox-4b.pdf", scale = 6, width = 10, units=c("cm"))

allEE4 <- alluvial_wide(select(clusterEE,Exposure_category, Maternal_exposure, Offspring_exposure), fill_by = 'first_variable',  order_levels = c('Abiotic habitat','Age', 'Chemical substance', 'Diet', 'Past experience', 'Physiological factor','Psychological factor', 'none' , 'independent' , 'diallel' , 'NA', 'no', 'yes'), stratum_label_size = 7,
                        col_vector_flow = col_vectorEE4, col_vector_value = col_vectorEE4) +
  theme_classic()+
theme(axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 20), axis.title.y = element_text(size = 20))+
  scale_x_discrete(expand = c(0,0.2))+
  labs(title= 'EcoEvo cluster', y = "Frequency")+
  theme(plot.title = element_text(size = 20, face="bold"))+
ggsave("Fig-EE-4b.pdf", scale = 6, width = 10, units=c("cm") )



```

```{r timeline of emprical studies}
# Preparing data for timeline figure
freq3 <-data.frame(xtabs(~Year + Exposure_category, empirical_clusters_expo))
freq3$Year <- as.numeric(as.character(freq3$Year))
str(freq3)

ggplot(freq3, aes(Year, Freq)) +
  geom_area(aes(fill = Exposure_category)) +
   scale_fill_manual(values = c("#6b452b", "#6fa6ab","#b0b54e", "#7081a1", "#edcb8a", "#70697d", "#3a3e3f", "#a2a39b",  "#1b1b1c","#a89985")) +
  scale_y_continuous(name="Frequency")+
  scale_x_continuous(breaks=c(1970, 1980, 1990, 2000, 2010, 2020))+
  theme_classic()+
  theme(aspect.ratio=0.4)+
        ggsave("Fig-2a.pdf")
```

## Visulasiation of the non-empirical layer of the map 

```{r timeline for non-empirical studies}
# Preparing data for timeline figure
freq2 <- data.frame(xtabs(~Year + Type, nonempirical)) 
freq2$Year <- as.numeric(as.character(freq2$Year))
str(freq2)

# Removing values with zeros 
freq23 <- filter(freq2, Freq !=0)

# Adding zeros at the begining of time series
first_years <- group_by(freq2, Type) %>%
               summarise(Year = min(Year) - 1) %>%
               filter(Year > 1970) %>%
               mutate(Freq = 0)

freq24 <- bind_rows(freq2, first_years) %>% arrange(Year, Type)

freq24$Type <- factor(freq24$Type, levels = c('commentary-perspective', 'narrative review','systematic review family','theoretical paper'))


ggplot(freq24, aes(x=Year, y=Freq,fill = Type) ) +
  geom_area() +
   theme_classic()+
      scale_fill_manual(values = c('theoretical paper' = "#141414", 'systematic review family' = "#828585" ,'narrative review' = "gray", 'commentary-perspective' = "#4f5157" ))+
  expand_limits(x = c(1960, 2020))+
    scale_x_continuous(breaks=c(1970,1980,1990,2000, 2010, 2020))+
  scale_y_continuous(breaks=c(0,10,20), name="Frequency")+
    theme(aspect.ratio=0.2)+
  ggsave("Fig-2b.pdf")

```

```{r focus of non-empircal studies}
# Preparing data for visualising focus of the studies
names(nonempirical)
nonempirical_focus <- data.frame(xtabs(~Taxon + Primary_focus + Secondary_focus, nonempirical))
nonempirical_focus <- filter(nonempirical_focus, Freq !=0)

nonempirical_focus$Taxon <- factor(nonempirical_focus$Taxon, levels = c('animals and plants', 'animals', 'mammals', 'humans'))

nonempirical_focus <- nonempirical_focus %>% arrange(Taxon, Primary_focus, -Freq)

nonempirical_focus <- nonempirical_focus %>% mutate(nonempirical_focus, proportion = Freq/sum(Freq)) 

nonempirical_focus <- nonempirical_focus %>% mutate(ymax = cumsum(proportion)) 

nonempirical_focus <- nonempirical_focus %>% mutate(ymin = ifelse(ymax!=0, lag(ymax), '0')) 

nonempirical_focus$ymin[is.na(nonempirical_focus$ymin)] <- 0
 
# Saving the transformed data
write.csv(nonempirical_focus, 'nonempirical_focus.csv')

# Making figure
ggplot(nonempirical_focus) + 
  geom_rect(aes(fill=Primary_focus, ymax=ymax, ymin=ymin, xmax=2.9, xmin=0.2)) +
  geom_rect(aes(fill=Secondary_focus, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
  xlim(c(0, 4)) + 
  theme(aspect.ratio=0.7) +
  coord_polar(theta="y")  +
facet_wrap(~ Taxon, nrow = 1) +
  scale_fill_manual(values = c('age'="#6fa6ab",'alcohol'="#b0b54e", 'metabolic disorders'="#edcb8a", 'assisted reproduction techniques'= "#c03728",'effects of drugs/toxins'= "#7081a1", 'ecology & evolution'= "#e2d51d", 'general'= "#828585",  'none'= "#3a3e3f",'offspring cancer'="#e68c7c",'proximate mechanisms'="#c83e74",'other'="#daa03d" ))+
  theme_void()+
  theme(legend.position="bottom")+
  theme(legend.title=element_blank())+
  ggsave("Fig-2c.pdf")


```

## Calculations of % for the main text

```{r trial}
# Data file
names(empirical_clusters)

empirical_clusters$cluster <- as.character(empirical_clusters$cluster)
empirical_clusters$cluster[empirical_clusters$cluster == "1"] <- "Med"
empirical_clusters$cluster[empirical_clusters$cluster == "2"] <- "Tox"
empirical_clusters$cluster[empirical_clusters$cluster == "3"] <- "EcoEvo"


# Stage of male exposure
# Separating males stages into rows
empirical_clusters_male_stage <- empirical_clusters %>% separate_rows(Exposure_stage, sep = ", ")
freq_male_stage <- data.frame(xtabs(~Exposure_stage + cluster, empirical_clusters_male_stage)) 
summary(freq_male_stage)

# Proportions of stages of exposure per cluster
freq4<-ddply(freq_male_stage,.(cluster),transform,prop=Freq/sum(Freq))
freq4

# Mate choice across the field 
names(empirical_clusters)
freq_mate_choice <- data.frame(xtabs(~Mating_in_study, empirical_clusters)) 
summary(freq_mate_choice)
freq_mate_choice <- freq_mate_choice %>% mutate(freq_mate_choice, proportion = Freq/sum(Freq))

# Maternal effects per cluster
names(empirical_clusters)
freq_maternal_effects <- data.frame(xtabs(~Maternal_effects + cluster, empirical_clusters)) 
summary(freq_maternal_effects)

freq6<-ddply(freq_maternal_effects,.(cluster),transform,prop=Freq/sum(Freq))
freq6

# Maternal exposure per cluster
names(empirical_clusters)
freq_maternal_exposure <- data.frame(xtabs(~Maternal_exposure + cluster, empirical_clusters)) 
summary(freq_maternal_exposure)

freq7<-ddply(freq_maternal_exposure,.(cluster),transform,prop=Freq/sum(Freq))
freq7 <- freq7 %>% arrange(Maternal_exposure, cluster)
freq7

# Offspring studied until adulthood per cluster
names(empirical_clusters)
freq_offspring_last_stage <- data.frame(xtabs(~Latest_offspring_stage + cluster, empirical_clusters)) 
summary(freq_offspring_last_stage)

freq8<-ddply(freq_offspring_last_stage,.(cluster),transform,prop=Freq/sum(Freq))
freq8 <- freq8 %>% arrange(Latest_offspring_stage, cluster)
freq8

# Accounting for offspring sex per cluster
names(empirical_clusters)
freq_offspring_sex <- data.frame(xtabs(~Sex_specific_effects + cluster, empirical_clusters)) 
summary(freq_offspring_sex)

freq9<-ddply(freq_offspring_sex,.(cluster),transform,prop=Freq/sum(Freq))
freq9 <- freq9 %>% arrange(cluster, Sex_specific_effects)
freq9


# Studying grand-offspring across the field 
names(empirical_clusters)
freq_grand_offspring <- data.frame(xtabs(~Grand_offspring_traits, empirical_clusters)) 
summary(freq_grand_offspring)
freq_grand_offspring <- freq_grand_offspring %>% mutate(freq_grand_offspring, proportion = Freq/sum(Freq))
freq_grand_offspring

# Offspring exposure per cluster
names(empirical_clusters)
freq_offspring_exposure <- data.frame(xtabs(~Offspring_exposure + cluster, empirical_clusters)) 
summary(freq_offspring_exposure)

freq10<-ddply(freq_offspring_exposure,.(cluster),transform,prop=Freq/sum(Freq))
freq10 <- freq10 %>% arrange(-Offspring_exposure, cluster)
freq10


```



## The Cophylogeny Dataset

### Table of the dataset



## Acknowledgements

xxx 

## R Session Information

```{r}
sessionInfo() %>% pander()
```

## References